### 2019-02-27 sections/introduction.tex
spelling

\todo{Alejandro: The introduction seems to be more about why Task-Oriented Programming
is nice and useful. Personally, I would like it to tell me another
story: given that some people find TOP useful (as shown by the many
examples), why should be care about formalizing it and which challenges
does it pose? I think this is what people from ICFP would care about more.}
Many applications these days are developed to support workflows in institutions and businesses.
Take for example expense declarations, order processing, and emergency management.
Some of these workflows occur on the boundary between organisations and customers,
like flight bookings or tax returns.
What they all have in common is
that they need to interact with different people (end users, tax officers, customers, etc.)
and they use information from multiple sources (input forms, databases, sensors, etc.).

>>>>

\todo{Alejandro: The introduction seems to be more about why Task-Oriented Programming
is nice and useful. Personally, I would like it to tell me another
story: given that some people find TOP useful (as shown by the many
examples), why should be care about formalising it and which challenges
does it pose? I think this is what people from ICFP would care about more.}
Many applications these days are developed to support workflows in institutions and businesses.
Take for example expense declarations, order processing, and emergency management.
Some of these workflows occur on the boundary between organisations and customers,
like flight bookings or tax returns.
What they all have in common is
that they need to interact with different people (end users, tax officers, customers, etc.)
and they use information from multiple sources (input forms, databases, sensors, etc.).
